Agents and you, a brief summary

### 2015-10-31 agents/summery.tex
finished the basic probablity stuff, on to the real markof stuffs.
I was right, slides were modified, so I deleted the note to avoid confusion.

So the agent comes accross a adopta method in the plan base $\Pi$, if
the associated believe of the goal is not true then you can start adding
it.

Note that in the slides the environment was also part of this action. But I
think this was a mistake, because in the paper of goaldynamic actions there
isn't a mention of an environment. Besides it doesn't make sense to include
the environment in an agent configuration.

\subsubsection{Applying planning goal rules}
The structure of a PG-rule in 2apl is as follows:

@@

\subsection{Exam}
 For a given decision problem with a certain
discount factor.A pure policy sufices.
Do policy iteration, (a single iteration), do value iteration
(single iteration).

>>>>

So the agent comes accross a adopta method in the plan base $\Pi$, if
the associated believe of the goal is not true then you can start adding
it.
\subsubsection{Applying planning goal rules}
The structure of a PG-rule in 2apl is as follows:

@@

\subsection{Total expectation}
The tower property, which is awesome:

Let $X$ and $Y$ be random variables then:

\[ E[E[X|Y]] = E[X] \]

The proof is in the slides.
\subsection{Exam}
 For a given decision problem with a certain
discount factor.A pure policy sufices.
Do policy iteration, (a single iteration), do value iteration
(single iteration).
